Describing the C-space of asynchronous periodic task using DIT

### 2013-07-26 dit-paper_ieee.tex
uunisort > uunifast
More rigorous explanation of formulation & added numerical example

			The authors of \cite{george2009characterization} give the following definition of the C-space:
			\begin{definition}
				For a given task system $\tau$ in which the $C_i$ are not known, the
				\textbf{C-space} is a region of $n$ dimensions (where each dimension denotes
				the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_0, \cdots, C_{n-1}\}$ in the C-space, $\tau$ is feasible.
			\end{definition}

@@

			A region of $\mathbb{N}^n$ can be described by a list of parametric linear
			constraints describing the convex hull of that region. In other words, a
			list of conditions which can unequivocally decide if a point is included in the region or not.\\

			For the synchronous case, the DBF test gives us a list of inequations
			on the WCET values of the task set which together are a necessary and
			sufficient condition of feasibility. They can all be written in the
			following way:
			\[
				\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq
				t_1 \leq t_2
			\]
			Note that for a given $t$, we have that the $n_i(t)$ are
			constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.\\

@@

	The value of the first DIT can be found by solving the following equation:
	\[
		t_d = \min
		\left( t \; s.t. \; \forall i:
			\left\{
				\begin{array}{c}
					t \equiv a_i \; (mod \; T_i) \\
					a_i \in [D_i, T_i]
				\end{array}
			\right.
		\right)
	\]

	\begin{remark} (from the definition):
		\begin{itemize}
			\item Contrary to other idle times, DITs are independent of the
			scheduling or the execution times of the jobs.
			\item In a feasible system, every DIT is an idle time.
			\item In a feasible system, the first DIT happens at the end of the
			first busy period.
			\item As $H$ is always a DIT in synchronous systems, we have at least $t_d
			\leqslant H$ in this case.
		\end{itemize}
	\end{remark}

	Every DIT being an idle instant, the execution of the system after a DIT does
	not depend on what happened before. Because the synchronous arrival pattern is
	the worst case [citation needed], it is sufficient for the DBF test to only
	consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\

	To summarize, we reduced the description of the C-space from an infinite number
	of constraints to only the inequations where $t_1 = 0$, $t_2 \leqslant t_d$ and
	values of $t_2$ correspond to job deadlines. Note that the number of
	constraints is still exponential in the number of tasks.

	\subsection{Our work}
		In this paper, we extend the work of \cite{george2009characterization} to the
		asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of
		the concept of DIT adapted to the asynchronous case called first periodic DIT
		($t_d$), along with an algorithm to find its value. In Section
		\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
		system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is
		sufficient to consider.

@@

@@

	We generated task systems by
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) equal to 3
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{CDF}, T_i]$, where the $CDF$ is called \emph{Constrained Deadline Factor}.
	\end{itemize}
	and then computed the value of the FPDIT.\\

@@

  The description we presented in Section \ref{sct:cspaceDescr} was general, and is thus still relevant. Therefore the C-space is still described by the following infinite number of constraints:$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$

@@

\begin{figure}[h]
$$z = \max C \, X$$
s.t.
\[
\begin{array}{rccc}
	A & X &\leq & B \\
	C & X &\leq & d + 1
\end{array}
\]
with
\[
	\begin{array}{ccc}
		A & : & [k,n] \text{ matrix}\\
		B & : & [1,n] \text{ matrix}\\
		C & : & [k,1] \text{ matrix}\\
		X & : & [1,n] \text{ matrix}\\
		d & : & \text{integer}
	\end{array}
\]
\caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as a ILP}
\end{figure}

@@

Such a linear problem can be solved by the simplex algorithm. However, here the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within. The naive method would be to directly test each constraints of the set against all the others, we present a similar method with an efficient preprocessing in Algorithm \ref{alg:prunRedun}.

\begin{algorithm}
\caption{Removing redundancy from CSPACE}
\label{alg:prunRedun}
	\begin{algorithmic}[1]
		\STATE $CSPACE$ : set of constraints
		\STATE $S \leftarrow \emptyset$
		\STATE \COMMENT{First pass - test $cstr$ against previous ones}
		\FOR{$cstr$ \textbf{in} $CSPACE$}
			\IF {$cstr$ is not redundant w.r.t. $S$}
				\STATE $S \leftarrow cstr$
			\ENDIF
		\ENDFOR
		\STATE \COMMENT{Second pass - test $cstr$ against every other}
		\FOR{$cstr$ \textbf{in} $S$}
			\STATE Remove $cstr$ from $S$
			\IF {$cstr$ is not redundant w.r.t. $S$}
				\STATE Put $cstr$ back into $S$
			\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

After doing this, no redundant constraints are left. However, this algorithm takes an exponential time in the number of constraints. An efficient initial description of $CSPACE$, as described in previous sections, is therefore preferred.\\

To summarize, we first reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise. After this correct but not efficient description of the C-SPACE, a linear integer approach removes the remaining redundancies.

>>>>

			The authors of \cite{george2009characterization} give the following definition of the C-space:
			\begin{definition}
				The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_0, \cdots, C_{n-1}\}$ in it, $\tau$ is feasible.
			\end{definition}

@@

			As explained in \cite{wolsey2000integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}). The constraints must be conditions which can unequivocally decide if a point is included in the region or not. In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$\footnote{For a formulation in $\mathbb{N}^n$ rather than in $\mathbb{N}_0^n$, the following inequations can be added to the formulation \[ C_i \geqslant 1 \; \forall i \]}.\\

			The DBF test gives us a list of inequations on the WCET values of the task set which together are a necessary and sufficient condition of feasibility. They can all be written in the following way:
			\[
				\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq
				t_1 \leq t_2
			\]
			Note that for a given $t$, we have that the $n_i(t)$ are
			constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.\\

@@

	\begin{remark} (from the definitions):
		\begin{itemize}
			\item Contrary to other idle times, DITs are independent of the
			scheduling or the execution times of the jobs.
			\item In a feasible system, every DIT is an idle time.
			\item In a feasible system, the first DIT happens after the end of the
			first busy period.
			\item As any $kH$ with $k \geqslant 0$ is a DIT in synchronous systems, we have at least $t_d
			\leqslant H$ in this case.
		\end{itemize}
	\end{remark}

	The value of the first DIT can be found by solving the following modular equation system:
	\[
		t_d = \min
		\left( t \; s.t. \; \forall i:
			\left\{
				\begin{array}{c}
					t > 0 \\
					t \equiv a_i \; (mod \; T_i) \\
					a_i \in [D_i, T_i]
				\end{array}
			\right.
		\right)
	\]
	The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.\\

	Every DIT being an idle instant, the execution of the system after a DIT does
	not depend on the execution before it. Because the synchronous arrival pattern is
	the worst case [citation needed], it is sufficient for the DBF test to only
	consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\

	To summarize, we reduced the description of the C-space from an infinite number
	of constraints to only those where $t_1 = 0$, $t_2 \leqslant t_d$ and
	values of $t_2$ correspond to job deadlines. Note that the number of
	constraints is still exponential in the number of tasks.

	\subsection{Our work}
		In this paper, we extend the work of \cite{george2009characterization} to the
		asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of
		the concept of DIT adapted to the asynchronous case called first periodic DIT
		($t_d$), along with an algorithm to find its value for any period values. In Section
		\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
		system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is
		sufficient to consider. In section ???, we present a simulation where we find that........

@@

	\subsection{Solving the modular system}

	PAUL PAUL PAUL ?

@@

	We generated task systems by
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) equal to 3
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{CDF}, T_i]$, where the $CDF$ is called \emph{Constrained Deadline Factor}.
	\end{itemize}
	and then computed the value of the FPDIT.\\

@@

  The description we presented in Section \ref{sct:cspaceDescr} was general, and is thus still relevant. Therefore the C-space is still accurately described by the following infinite number of constraints:$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$

@@

\begin{figure}[h]
$$z = \max C \, X$$
s.t.
\[
\begin{array}{rccc}
	A & X &\leq & B \\
	C & X &\leq & d + 1
\end{array}
\]
with
\[
	\begin{array}{ccc}
		A & : & [k,n] \text{ matrix}\\
		B & : & [1,n] \text{ matrix}\\
		C & : & [n,1] \text{ matrix}\\
		X & : & [1,n] \text{ matrix}\\
		d & : & \text{integer}
	\end{array}
\]
\caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as an ILP}
\end{figure}

@@

Such a linear problem can be solved by the simplex algorithm. However, here the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within. The naive method would be to directly test each constraints of the set against all the others, we present a similar method with an efficient preprocessing in Algorithm \ref{alg:prunRedun}.\\

\begin{algorithm}
\caption{Removing redundancy from CSPACE}
\label{alg:prunRedun}
	\begin{algorithmic}[1]
		\STATE $CSPACE$ : set of constraints
		\STATE $S \leftarrow \emptyset$
		\STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
		\FOR{$cstr$ \textbf{in} $CSPACE$}
			\IF {$cstr$ is not redundant w.r.t. $S$}
				\STATE $S \leftarrow cstr$
			\ENDIF
		\ENDFOR
		\STATE \COMMENT{$2^{nd}$ pass: test each $cstr$ against every other}
		\FOR{$cstr$ \textbf{in} $S$}
			\STATE Remove $cstr$ from $S$
			\IF {$cstr$ is not redundant w.r.t. $S$}
				\STATE Put $cstr$ back into $S$
			\ENDIF
		\ENDFOR
		\RETURN{S}
	\end{algorithmic}
\end{algorithm}

After doing this, no redundant constraints are left. However, this algorithm takes an exponential time in the number of constraints. An efficient initial description of $CSPACE$, as given by the methods described in previous sections, is therefore preferred.\\

To summarize, we first reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise. After this correct but not efficient description of the C-SPACE, a linear integer approach removes the remaining redundancies. Note that

\subsection{Numerical Example}

Consider the following task system

		\begin{center}
		\begin{tabular}{|r|c|c|c|c|}
		 \hline
		  & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
		 \hline
		 $\tau_1$ & 5 & $C_1$ & 4 & 9\\
		 \hline
		 $\tau_2$ & 0 & $C_2$ & 12 & 14\\
		 \hline
		\end{tabular}
		\end{center}
		~\\

The FPDIT happens at $t=12$ and $H = 126$. The study interval using the FPDIT is thus $[12, 138]$, which contains 261 intervals $[a,d]$ with $a$ being the arrival of a job, $d$ being the deadline of a job, and $12 \leqslant a < d \leqslant 138$. For comparison, the more pessimistic study interval is $[5, 257]$ which yields 1006 intervals.\\

We now apply the
